### 2016-02-11 prepReport/theorBack.tex
Added Chapter 5. Still needs polishing

\subsubsection{Training -- SPSA}\label{sec:training_lstm}
Since this work aims to perform on-chip learning, it is important to find a suitable learning scheme. Since I am aiming at an hardware implementation, and although the memory resources of nowadays FPGAs are abundant, one must find an algorithm that uses the less memory as possible (at the smallest performance cost possible), in order to use the additional memory, for instance, to add additional LSTM cells that can improve the performance of our system. 
That being said, we see that the usual training algorithms for LSTM cells -- i.e. Real-Time Recurrent Learning (RTRL), Truncated Backpropagation Through Time (BPTT) or a mixture of both~\cite{Graves05}~\cite{Hoch97}~\cite{Greff15} -- usually involve the storage of the deltas of each layer for every time instant in the training epoch (from $0$ to $T$), which is a highly non-scalable solution both in terms of memory and performance. A most efficient approach to training times series dependant structures like LSTM is the use of \textbf{Simultaneous Perturbation Stochastic Approximation} (SPSA)~\cite{Spall98}. The weight update for the $i$-th weight at the time step $t$ is given by

@@

\begin{equation}\label{eq:spsa_updateRule}
    w_i^{(t+1)} = w_i^{(t)} - \eta \Delta w_i^{(t)}
\end{equation}
where $\eta$ is the learning rate, and $\Delta w_i^{(t)}$ is the update for the $i$-th weight evaluated in~\ref{eq:spsa_weightUpdate}.
According to the analysis performed in~\cite{Maeda05}, performing a second-order Taylor expansion at $\mb{w} = \mb{w}^{(t)}$, and taking the expected value of the equation, we get that

\begin{equation}\label{eq:spsa_gradProof}
    E(\Delta w_i^{(t)}) = \frac{\partial J(\mb{w}^{(t)})}{\partial w_i^{(t)}}
\end{equation}
that is, the weight update approximates the gradient of the cost function relative to that weight, and so the learning rule is a special form of \textit{Stochastic Gradient Descent}.

>>>>

\subsubsection{Training -- SPSA}\label{sec:training_lstm}
Since this work aims to perform on-chip learning, it is important to find a suitable learning scheme. Since I am aiming at an hardware implementation, and although the memory resources of nowadays FPGAs are abundant, one must find an algorithm that uses the less memory as possible (at the smallest performance cost possible), in order to use the additional memory, for instance, to add additional LSTM cells that can improve the performance of our system. 
That being said, we see that the usual training algorithms for LSTM cells -- i.e. Real-Time Recurrent Learning (RTRL), Truncated Backpropagation Through Time (BPTT) or a mixture of both~\cite{Graves05}~\cite{Hoch97}~\cite{Greff15} -- usually involve the storage of the deltas of each layer for every time instant in the training epoch (from $0$ to $T$), which is a highly non-scalable solution both in terms of memory and performance. A most efficient approach to training times series dependant structures like LSTM is the use of \textbf{Simultaneous Perturbation Stochastic Approximation} (SPSA)~\cite{Spall98}.  The main idea of this technique is, instead of explicitly evalute the gradients for the cost function at each time step, perform a random walk in the neighbourhood of the current weight matrix, in the weight space, and approximate the new weight update by the approximation of the gradient of the cost function that resulted from that random walk. The weight update for the $i$-th weight at the time step $t$ is given by

@@

\begin{equation}\label{eq:spsa_updateRule}
    w_i^{(t+1)} = w_i^{(t)} - \eta \Delta w_i^{(t)}
\end{equation}
where $\eta$ is the learning rate, and $\Delta w_i^{(t)}$ is the update for the $i$-th weight evaluated in~\ref{eq:spsa_weightUpdate}.
According to the analysis performed in~\cite{Maeda05}, performing a two-term Taylor expansion at $\mb{w} = \mb{w}^{(t)}$, and taking the expected value of the equation, we get that there is a $\mb{w}_{S1}$ so that

\begin{equation}\label{eq:taylor}
    \Delta w_i^{(t)} = s_i^{(t)} (\mb{s}^{(t)})^T \frac{\partial J(\mb{w}^{(t)})}{\partial \mb{w}} +
                        \frac{c s_i^{(t)}}{2} (\mb{s}^{(t)})^T \frac{\partial^2 J(\mb{w}^{(t)})}{\partial \mb{w}^2}  (\mb{s}^{(t)}) 
\end{equation}
If the random sign vector $\mb{s}^{(t)}$ is chosen carefully so that the expected value of the vector at the $i$-th position is zero, $E(s_i^{(t)})$, and the signs of two different components $i$ and $j$, at different time-steps, are independent (i.e. $E(s_i^{(t_1)}s_j^{(t_2)}) = \delta_{ij}\delta_{t_1 t_2}$, equation~\ref{eq:taylor} reduces to

\begin{equation}\label{eq:spsa_gradProof}
    E(\Delta w_i^{(t)}) = \frac{\partial J(\mb{w}^{(t)})}{\partial w_i^{(t)}}
\end{equation}
that is, the \emph{expected value} of the weight update approximates the gradient of the cost function relative to that weight, and so the learning rule is a special form of \textit{Stochastic Gradient Descent}.

### 2016-02-11 prepReport/workPlan.tex
Added Chapter 5. Still needs polishing

\subsection{Hardware Resources}
The main hardware resource that I will use for my solution is the \textbf{Xilinx\textregistered~ Zedboard}, whose core is a Zynq-7000 System-on-Chip that features both an FPGA core and an ARM \textregistered~ Cortex\texttrademark~-A9 processor. It is an FPGA development board that features several I/O interfaces such as Etherner, HDMI output, VGA output, Audio IOs, USB and UART, among other capabilites, making it easy to prototype additional features to the core design (i.e. for building the note transcription system of~\cite{Bock12}, and to make it operate in real-time, I would need an audio input, which I can easily get from the Audio IO, without investing time in connecting the codec and programming the FPGA to interface it).

>>>>

\subsection{Hardware Resources}
The main hardware resource that I will use for my solution is the \textbf{Xilinx\textregistered~ Zedboard} (Figure~\ref{fig:zedboard}, whose core is a Zynq-7000 System-on-Chip that features both an FPGA core and an ARM \textregistered~ Cortex\texttrademark~-A9 processor. It is an FPGA development board that features several I/O interfaces such as Etherner, HDMI output, VGA output, Audio IOs, USB and UART, among other capabilites, making it easy to prototype additional features to the core design (i.e. for building the note transcription system of~\cite{Bock12}, and to make it operate in real-time, I would need an audio input, which I can easily get from the Audio IO, without investing time in connecting the codec and programming the FPGA to interface it).

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/zedboard.jpg}
    \caption{The Zedboard FPGA Development Board. Source: \href{http://www.xilinx.com}{Xilinx}}
    \label{fig:zedboard}
\end{figure}
